### 2019-03-16 micro4_1.tex
Micro

\textbf{Solution}
\begin{enumerate}
	\item The tree of this game is depicted below.
		\begin{figure}[H]
		\centering
		\includegraphics[width=0.8\textwidth]{plotdraft}
		\caption{}\label{fig1}
	\end{figure}
Since $D^L < 0 < D^H$ the entrant in case of low demand will always choose not enter, and in case of high demand will always choose enter. The incumbent hence should solve the following optimization problems:
\begin{align*}
\underset{m \in [0, M^H]}{\max}\ m+D^H\ \text{ if demand is high}\\
\underset{m \in [0, M^L]}{\max}\ m+M^L\ \text{ if demand is low}\\
\end{align*}
That's why the optimal strategy for incumbent is to choose $M^H$ and $M^L$ in case of high and low demand respectively.
\item The tree of this game is depicted below
		\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{plotdraft}
	\caption{}\label{fig2}
\end{figure}
Denote the belief of the entrant that he is at the high demand case as $\omega$. If incumbent chooses $M^H$ as a profit for high demand case and $M^L$ as a profit for the low demand case, then $\omega = 1$, that means that the strategy of the entrant consistent with such a belief is choosing not enter if $m = M^H$ and enter if $m = M^L$. But since $D^H < M^L$ the incumbent has incentive to deviate and choose $M^L$ if demand is high in order to prevent the entrant from entry and obtain $M^L + M^H$ instead of $M^H + D^H$. Thus, the "honest" strategy is not an equilibrium one for the incumbent.
\item The tree of the game is depicted below
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{plotdraft}
	\caption{}\label{fig3}
\end{figure}
Denote $\omega$ is a condition belief of the entrant that the demand is high. Assume $\omega = p: pD^H + (1-p)D^L < 0$. For such a belief the optimal strategy for the entrant is enter once the incumbent's profit if $M^H$ and not enter otherwise (once it is $M^L$). The incumbent's strategy hence is to choose $M^L$ in both cases because
\begin{align*}
M^H + D^H < M^H + M^L
\end{align*}
Moreover $\omega = p$ is consistent with such a strategy of the incumbent. Thus, the equilibrium is:
\begin{align*}
&\text{Incumbent : } \left\{M^L, M^L\right\}\\
&\text{Entrant : } \left\{\text{enter if incumbent's profit is } M^H \text{ not enter if it is } M^L\right\}\\
&\text{Entrant's belief : } (p, 1-p)
\end{align*}
This is a pooling equilibrium.
\end{enumerate}
\section*{2\ Beer and Quiche}
Nick wakes up and feels like fighting. He goes to a local pub in a hope of finding a target
there. Indeed, there he sees a man (called Paul) ordering a breakfast. Nick has seen Paul
before, but never talked to him. Nick knows that Paul can be of two types: Wimp or
Surly. Surly type is always eager to fight, and Nick does not want to fight with a Surly
type. In turn, Wimp is weak and easy to fight with, so Nick would be eager to release
his anger on a Wimp type. However, Nick does not know Paul's type exactly, he only
knows that the probability of each type is 0.5. Further, Nick has read in a book called
"Real Men Don't Eat Quiche" by Bruce Feirstein that surly people typically have beer
for breakfast, while wimp guys prefer ordering a quiche. Nick observes what Paul has
for breakfast, and decides whether to fight or pass. The payoffs are summarized in the
matrices below, where the strategies of Nick are in the columns, and the ones of Paul are
in the rows

@@

	If we denote belief for Paul of coming across the surly type condition on the fact that Paul gets the beer as $\omega$ and  belief for Paul of coming across the wimp type condition on the fact that Paul gets the quiche as $\lambda$, then the separating equilibrium is:
	\begin{align*}
	&\text{Paul : } \{beer, quiche\}\\
	&\text{Nick : } \{pass, fight\}\\
	& \omega = 1, \lambda = 0
	\end{align*}
	(first action of Paul corresponds to surly type and the second to wimp type, while first action of Nick corresponds to Paul orders beer and the second corresponds to Paul orders quiche)
	\item Assume $\omega = \frac{1}{2} > \frac{1}{3}$ in this case
	\begin{align*}
	2\omega + 1 - \omega < 0
	\end{align*}
	that means that Nich chooses $pass$ once Paul gets beer. If $\lambda > \frac{1}{3}$ then $-2\lambda + 1 - \lambda < 0$ which means that Nick chooses to pass even if Paul gets quiche. Since $c > 0$, $1 - c < 1$ and Paul should choose quiche for wimp type. In case $\lambda < \frac{1}{3}$ Nick chooses to fight once Paul gets quiche, as a result if $-1 \le 1 - c$ i.e. $c \le 2$ even wimp type will choose beer.
	Thus, the equilibrium is:
	\begin{align*}
	&\text{Paul : } \{beer, beer\}\\
	&\text{Nick : } \{pass, fight\}\\
	& \omega = \frac{1}{2}, \lambda < \frac{1}{3}
	\end{align*}
	(again, first action of Paul corresponds to surly type and the second to wimp type, while first action of Nick corresponds to Paul orders beer and the second corresponds to Paul orders quiche)
	\item It does not satisfy the intuitive criterion. It makes no sense for wimpish Paul to deviate, if $c \le 2$, whereas a surly Paul is indifferent between beer and quiche and in principle can deviate, that means that Nick should believe that if Paul gets quiche, he is surly and as a result he should avoid fighting, but being aware of that wimpish Paul chooses $quiche$, and the equilibrium is broken.
\end{enumerate}
\section*{3\ Education}
Consider Spence's job-marker signalling model. There are two firms on the market, and
two types of worker, $\theta_H$ and $\theta_L$; $\theta_H > \theta_L > 0$. The probability of type $\theta_H$ is $Prob(\theta =
\theta_H) = \lambda$, and is common knowledge. The worker knows his productivity and chooses
education $e \ge 0$. Education is productive: the productivity of a worker of type $\theta_i$ with
education $e$ is given by:
\begin{align*}
\theta_i + e
\end{align*}
The firms observe $e$ and simultaneously make the worker a wage offer. Then the worker
accepts the highest of the wages, $w$. The payoff of the worker of productivity $\theta_i, i = L, H,$ is:
\begin{align*}
w - c(\theta_i, e)
\end{align*}
where $c(\theta_i, e)$ is the cost of education $e$ for the worker of ability $\theta_i$,
\begin{align*}
c(\theta_i, e) = \frac{e^2}{2\theta_i}
\end{align*}
The payoff of the firm that hires the worker of type $\theta_i$ with education $e$ at the wage $w$ is
\begin{align*}
\theta_i + e - w
\end{align*}
Assume also that the firms have the same beliefs about the worker's productivity off equilibrium path. 
\begin{enumerate}
\item Consider the full information case, in which firms observe the type of the worker. What are the wages $w^*_L, w^*_H$, and the levels of education $e^*_L, e^*_H$ under this scenario?

@@

	So, when the productivity of the low type is very low compare to that of high type, costs of education are very high for low type workers and it is not optimal for them to pretend to be a high type, which means that low type workers choose $e^*_L = \theta_L$ and high type workers choose $e^*_H = \theta_H$ and firms perfectly distinguish between types.

@@

	\lambda \theta_L + (1 - \lambda) \theta_H, e = 0\\

@@

	\max\left\{ \underset{e > 0}{\max}\ \theta_L + e - \frac{e^2}{2\theta_H}, \lambda \theta_L + (1 - \lambda) \theta_H \right\} = \max\left\{\theta_L + \frac{\theta_H}{2}, \lambda \theta_L + (1 - \lambda) \theta_H \right\}

@@

	If $\lambda \le \frac{1}{2}$ then $\theta_L + \frac{\theta_H}{2} > \lambda \theta_L + (1 - \lambda)\theta_H$ and that means that high type will deviate and choose positive $e^*_H = \theta_H$ level of education, i.e. $e_p = 0$ is not supportable.
	\item No, they cannot be. Firstly, obviously that the greatest amount of efforts the workers can spend on education at any pooling equilibria cannot exceed $\bar{e}$ (see Fig. \ref{fig5}) because for any other education level $e > \bar{e}$ and respective equilibrium wage level $w(e) = \lambda \theta_H + (1 - \lambda)\theta_L + e$ the low type worker prefers $e = 0$. (here $\bar{e} = \theta_L\left(1 + \sqrt{1 + \frac{2\lambda(\theta_H - \theta_L)}{\theta_L}}\right) > \theta_L$)

@@

		\caption{}\label{fig5}

@@

Suppose now that the pooling equilibrium is attained at education level $e' < \bar{e}$ (see Fig. \ref{fig5}). The corresponding indifference curves and wage schedule is depicted on the Fig. \ref{fig5}. Both types are maximizing their utilities, given the wage schedule and equilibrium wages are consistent with beliefs. And this pooling equilibrium Pareto dominates the one with $e = \bar{e}$ (and also each equilibrium with $e' < e < \bar{e}$) because firms have the same zero expected profit, but both types attain higher indifference curves and consequently higher utility levels at $e'$. However, there always exists an education level $\underline{e} = \theta_H$ (which is wlog $< \bar{e}$) such that indifference curve of high type is tangent to the line $\lambda \theta_H + (1 - \lambda)\theta_L + e$ at this point (see Fig. \ref{fig5}). And each pooling  equilibrium level of education $e'' < \underline{e}$ will yield the high type worker strictly less utility. Since each point at line $\lambda \theta_H + (1 - \lambda) \theta_L + e$ for $e < \underline{e}$ corresponds to lower indifference curve for high type. Similarly for low type workers there exists an education level $\underline{\underline{e}} = \theta_L$ such that indifference curve of low type is tangent to the line $\lambda \theta_H + (1 - \lambda)\theta_L + e$ at this point (see Fig. \ref{fig5}). And each pooling  equilibrium level of education $e''' < \underline{\underline{e}}$ will yield the low type worker strictly less utility. Since each point at line $\lambda \theta_H + (1 - \lambda) \theta_L + e$ for $e < \underline{\underline{e}}$ corresponds to lower indifference curve for low type. As a result, there is a full Pareto order for pooling equilibrium for $e \in [\theta_H, \bar{e}]$ and for $e \in [0, \theta_L]$, for $e \in (\theta_L, \theta_H)$ there is no Pareto order, since some pooling equilibria are better for low type, but are worse for high type and vice-versa.

Case $\theta_H > \bar{e}$ is analogous, for $e \in (\theta_L, \theta_H)$ equilibria cannot be Pareto ranked.
\item Dominance requirement requires firms to prescribe positive $\mu(e)$ only to such $e$ that is not a strictly dominated action for high type. In the sense that there is no action $e'$ which yields the high type strictly greater payoff regardless of what equilibrium wages are. Assumption that $\Omega$ in non-empty means that firstly $\theta_H < \bar{e}$ and on the top of that the indifference curve of high type, which goes through $(\bar{e}, \theta_H + \bar{e})$ lies below the indifference curve which is tangent to the line $\lambda \theta_H + (1 - \lambda) \theta_L$ at the point $\theta_H$ (see Fig. \ref{fig6}) because otherwise, the high type chooses the level $\max\ \{\theta_H, \bar{e}\}$ and low type chooses $0$ and $\Omega$, the set of pooling equilibria, is empty.
	\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{plotdraft}
	\caption{}\label{fig6}
\end{figure} 
The highest pooling equilibrium payoff for the high type is delivered at the education level $e = \theta_H$. In our case this equilibrium belongs to $\Omega$ because neither of types have $e = \theta_H$ as a strictly dominated action. On the Fig. \ref{fig6} there is a wage schedule for which $e_H = e_L = \theta_H$ is the best response for both types (i.e. there is no action which strictly dominates this action).
	\end{enumerate}
\end{enumerate}
\section*{4\ Exams}
Karen would like her friend Tim to pass his exams. Tim may choose to work at a
private cost of $c$. If he slacks, he fails. If he works, he passes with probability $\theta$. Hence $\theta$
is Tim's $ability$. If he passes, Karen receives a private benefit of $V > 0$ and Tim receives
a private benefit of $U > 0$.
Karen offers to pay a reward $b \in [0; V]$ to Tim if and only if he passes. Hence Karen
receives a payoff $V-b$ if Tim passes, and zero otherwise. Tim receives a payoff of zero if
he slacks, $-c$ if he works and fails, and $U + b-c$ if he works and passes. For simplicity,
assume that Tim will choose to work whenever he is otherwise indifferent between working
and slacking.
Tim's ability is initially unknown; $\theta_H$ with probability $\alpha$ and $\theta_L$ otherwise where
\begin{align*}
1 > \theta_H > \theta_L > 0, [\alpha \theta_H + (1-\alpha)\theta_L] U < c < \theta_L(U + V ) \text{ and } c < \theta_H U
\end{align*}
We refer to Tim's beliefs about $\theta$ as his "confidence". Begin by assuming that neither
player observes $\theta$. Hence Karen begins by choosing a bonus $b$. Tim observes this bonus,
and then chooses whether to work
\begin{enumerate}
	\item What bonus will Karen choose to offer?

@@

@@

In addition assume that we have a separating equilibrium i.e. the wage inequality is $\theta_H - \theta_L$ and moreover let us use the intuitive criterion refinement which eliminates all pooling equilibria. Since indifference curves of low type workers become flatter, it is now becomes profitable for them to deviate and to pretend to be workers of high productivity. In this case either firms become unable to distinguish between the types and offer a single wage for all types (pooling equilibrium) and as a result, inequality decreases to 0, or workers of high type just increase their level of education (starting to pursue PhD for example) and firm still are able to distinguish between types and offer different wages, hence the wage inequality remains unchanged.

\end{document}

>>>>

\textbf{Solution}
\begin{enumerate}
	\item The tree of this game is depicted below.
		\begin{figure}[H]
		\centering
		\includegraphics[width=0.8\textwidth]{plotdraft}
		\caption{}\label{fig1}
	\end{figure}
Since $D^L < 0 < D^H$ the entrant in case of low demand will always choose not enter, and in case of high demand will always choose enter. The incumbent hence should solve the following optimization problems:
\begin{align*}
\underset{m \in [0, M^H]}{\max}\ m+D^H\ \text{ if demand is high}\\
\underset{m \in [0, M^L]}{\max}\ m+M^L\ \text{ if demand is low}\\
\end{align*}
That's why the optimal strategy for incumbent is to choose $M^H$ and $M^L$ in case of high and low demand respectively.
\item The tree of this game is depicted below
		\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{plotdraft}
	\caption{}\label{fig2}
\end{figure}
Denote the belief of the entrant that he is at the high demand case as $\omega$. If incumbent chooses $M^H$ as a profit for high demand case and $M^L$ as a profit for the low demand case, then $\omega = 1$, that means that the strategy of the entrant consistent with such a belief is choosing not enter if $m = M^H$ and enter if $m = M^L$. But since $D^H < M^L$ the incumbent has incentive to deviate and choose $M^L$ if demand is high in order to prevent the entrant from entry and obtain $M^L + M^H$ instead of $M^H + D^H$. Thus, the "honest" strategy is not an equilibrium one for the incumbent.
\item The tree of the game is depicted below
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{plotdraft}
	\caption{}\label{fig3}
\end{figure}
Denote $\omega$ is a condition belief of the entrant that the demand is high. Assume $\omega = p: pD^H + (1-p)D^L < 0$. For such a belief the optimal strategy for the entrant is enter once the incumbent's profit is $M^H$ and not enter otherwise (once it is $M^L$). The incumbent's strategy hence is to choose $M^L$ in both cases because
\begin{align*}
M^H + D^H < M^H + M^L
\end{align*}
Moreover $\omega = p$ is consistent with such a strategy of the incumbent. Thus, the equilibrium is:
\begin{align*}
&\text{Incumbent : } \left\{M^L, M^L\right\}\\
&\text{Entrant : } \left\{\text{enter if incumbent's profit is } M^H \text{ not enter if it is } M^L\right\}\\
&\text{Entrant's belief : } (p, 1-p)
\end{align*}
This is a pooling equilibrium.
\end{enumerate}
\section*{2\ Beer and Quiche}
Nick wakes up and feels like fighting. He goes to a local pub in a hope of finding a target
there. Indeed, there he sees a man (called Paul) ordering a breakfast. Nick has seen Paul
before, but never talked to him. Nick knows that Paul can be of two types: Wimp or
Surly. Surly type is always eager to fight, and Nick does not want to fight with a Surly
type. In turn, Wimp is weak and easy to fight with, so Nick would be eager to release
his anger on a Wimp type. However, Nick does not know Paul's type exactly, he only
knows that the probability of each type is 0.5. Further, Nick has read in a book called
"Real Men Don't Eat Quiche" by Bruce Feirstein that surly people typically have beer
for breakfast, while wimp guys prefer ordering a quiche. Nick observes what Paul has
for breakfast, and decides whether to fight or pass. The payoffs are summarized in the
matrices below, where the strategies of Nick are in the columns, and the ones of Paul are
in the rows

@@

	If we denote belief for Paul of coming across the surly type condition on the fact that Paul gets the beer as $\omega$ and  belief for Paul of coming across the wimp type condition on the fact that Paul gets the quiche as $\lambda$, then the separating equilibrium is:
	\begin{align*}
	&\text{Paul : } \{beer, quiche\}\\
	&\text{Nick : } \{pass, fight\}\\
	& \omega = 1, \lambda = 0
	\end{align*}
	(first action of Paul corresponds to surly type and the second to wimp type, while first action of Nick corresponds to Paul orders beer and the second corresponds to Paul orders quiche)
	\item Assume $\omega = \frac{1}{2} > \frac{1}{3}$ in this case
	\begin{align*}
	2\omega + 1 - \omega < 0
	\end{align*}
	that means that Nick chooses $pass$ once Paul gets beer. If $\lambda > \frac{1}{3}$ then $-2\lambda + 1 - \lambda < 0$ which means that Nick chooses to pass even if Paul gets quiche. Since $c > 0$, $1 - c < 1$ and Paul should choose quiche for wimp type. In case $\lambda < \frac{1}{3}$ Nick chooses to fight once Paul gets quiche, as a result if $-1 \le 1 - c$ i.e. $c \le 2$ even wimp type will choose beer.
	Thus, the equilibrium is:
	\begin{align*}
	&\text{Paul : } \{beer, beer\}\\
	&\text{Nick : } \{pass, fight\}\\
	& \omega = \frac{1}{2}, \lambda < \frac{1}{3}
	\end{align*}
	(again, first action of Paul corresponds to surly type and the second to wimp type, while first action of Nick corresponds to Paul orders beer and the second corresponds to Paul orders quiche)
	\item It does not satisfy the intuitive criterion. It makes no sense for wimpish Paul to deviate, if $c \le 2$, whereas a surly Paul is indifferent between beer and quiche and in principle can deviate, that means that Nick should believe that if Paul gets quiche, he is surly and as a result he should avoid fighting, but being aware of that wimpish Paul chooses $quiche$, and the equilibrium is broken.
\end{enumerate}
\section*{3\ Education}
Consider Spence's job-marker signalling model. There are two firms on the market, and
two types of worker, $\theta_H$ and $\theta_L$; $\theta_H > \theta_L > 0$. The probability of type $\theta_H$ is $Prob(\theta =
\theta_H) = \lambda$, and is common knowledge. The worker knows his productivity and chooses
education $e \ge 0$. Education is productive: the productivity of a worker of type $\theta_i$ with
education $e$ is given by:
\begin{align*}
\theta_i + e
\end{align*}
The firms observe $e$ and simultaneously make the worker a wage offer. Then the worker
accepts the highest of the wages, $w$. The payoff of the worker of productivity $\theta_i, i = L, H,$ is:
\begin{align*}
w - c(\theta_i, e)
\end{align*}
where $c(\theta_i, e)$ is the cost of education $e$ for the worker of ability $\theta_i$,
\begin{align*}
c(\theta_i, e) = \frac{e^2}{2\theta_i}
\end{align*}
The payoff of the firm that hires the worker of type $\theta_i$ with education $e$ at the wage $w$ is
\begin{align*}
\theta_i + e - w
\end{align*}
Assume also that the firms have the same beliefs about the worker's productivity off equilibrium path. 
\begin{enumerate}
\item Consider the full information case, in which firms observe the type of the worker. What are the wages $w^*_L, w^*_H$, and the levels of education $e^*_L, e^*_H$ under this scenario?

@@

	So, when the productivity of the low type is very low compare to that of high type, costs of education are very high for low type workers and it is not optimal for them to pretend to be a high type, which means that low type workers choose $e^*_L = \theta_L$ and high type workers choose $e^*_H = \theta_H$ and firms perfectly distinguish between types. On the figure below two examples are provided where the PBE which replicates the full information outcome is possible and where not.
		\caption{Left: low type has profitable deviation; Right: low type does not have a profitable deviation}\label{fig7}

@@

	\lambda \theta_H + (1 - \lambda) \theta_L, e = 0\\

@@

	\max\left\{ \underset{e > 0}{\max}\ \theta_L + e - \frac{e^2}{2\theta_H}, \lambda \theta_H + (1 - \lambda) \theta_L \right\} = \max\left\{\theta_L + \frac{\theta_H}{2}, \lambda \theta_H + (1 - \lambda) \theta_L \right\}

@@

	If $0 \le \lambda \le \frac{1}{2}$ then $\theta_L + \frac{\theta_H}{2} > \lambda \theta_H + (1 - \lambda)\theta_L$ and that means that high type will deviate and choose positive $e^*_H = \theta_H$ level of education, i.e. $e_p = 0$ is not supportable. Figure below illustrates the case.

@@

		\caption{Unsupportable $e_p = 0$}\label{fig8}

@@

	\item No, they cannot be. The levels of education which maximize workers' utilities provided that firms pay a wage $\lambda \theta_H + (1 - \lambda) \theta_l + e$ are $e_H = \theta_H, e_L = \theta_L$. Since $\theta_H > \theta_L$ all pooling equilibria with education level above $\theta_H$ are Pareto ordered because decreasing of $e$ benefits both types of workers and firm still earn zero profit. However, equilibria with education level between $\theta_L$ and $\theta_H$ are not Pareto ordered because once $e^*_p \to \theta_L$ the high type becomes worse-off and the low type becomes better-off.
\item Dominance requirement requires firms to prescribe positive $\mu(e)$ only to such $e$ that is not a strictly dominated action for high type. In the sense that there is no action $e'$ which yields the high type strictly greater payoff regardless of what equilibrium wages are. Assumption that $\Omega$ in non-empty means that firstly $\theta_H < \bar{e}$ (where $\bar{e}$ is the highest possible amount of education the low type worker obtains in any pooling equilibria) and on the top of that the indifference curve of high type, which goes through $(\bar{e}, \theta_H + \bar{e})$ lies below the indifference curve which is tangent to the line $\lambda \theta_H + (1 - \lambda) \theta_L$ at the point $\theta_H$ (see Fig. \ref{fig6}) because otherwise, the high type chooses the level $\max\ \{\theta_H, \bar{e}\}$ and low type chooses $0$ and $\Omega$, the set of pooling equilibria, is empty.
	\caption{}\label{fig6}
The highest pooling equilibrium payoff for the high type is delivered at the education level $e = \theta_H$. In our case this equilibrium belongs to $\Omega$ because neither of types have $e = \theta_H$ as a strictly dominated action. On the Fig. \ref{fig6} there is a wage schedule for which $e_H = e_L = \theta_H$ is the best response for both types (i.e. there is no action which strictly dominates this action).
\section*{4\ Exams}
Karen would like her friend Tim to pass his exams. Tim may choose to work at a
private cost of $c$. If he slacks, he fails. If he works, he passes with probability $\theta$. Hence $\theta$
is Tim's $ability$. If he passes, Karen receives a private benefit of $V > 0$ and Tim receives
a private benefit of $U > 0$.
Karen offers to pay a reward $b \in [0; V]$ to Tim if and only if he passes. Hence Karen
receives a payoff $V-b$ if Tim passes, and zero otherwise. Tim receives a payoff of zero if
he slacks, $-c$ if he works and fails, and $U + b-c$ if he works and passes. For simplicity,
assume that Tim will choose to work whenever he is otherwise indifferent between working
and slacking.
Tim's ability is initially unknown; $\theta_H$ with probability $\alpha$ and $\theta_L$ otherwise where
1 > \theta_H > \theta_L > 0, [\alpha \theta_H + (1-\alpha)\theta_L] U < c < \theta_L(U + V ) \text{ and } c < \theta_H U
We refer to Tim's beliefs about $\theta$ as his "confidence". Begin by assuming that neither
player observes $\theta$. Hence Karen begins by choosing a bonus $b$. Tim observes this bonus,
and then chooses whether to work
	\item What bonus will Karen choose to offer?

@@

	\item Single crossing condition means that once cost of work increases the low type Tim needs higher bonus compensation to preserve the same utility level than the high type Tim. Expected utility levels of both types are the following:
	u_H = \begin{cases}
	(U + b) \theta_H - c, \text{ if Tim works}\\
	0, \text{if Tim slacks}
	\end{cases}\\
	u_L = \begin{cases}
	(U + b) \theta_L - c, \text{ if Tim works}\\
	0, \text{if Tim slacks}
	\end{cases}\\
	Since $\frac{1}{\theta_H} < \frac{1}{\theta_L}$ then for high levels of utility single crossing condition holds. However, for example for utility level $0$ and for $c < U \theta_L$ (see Fig. \ref{fig9})as we can see utility curves coincide, i.e. the single crossing condition does not hold.
		\caption{}\label{fig9}

@@

In addition assume that we have a separating equilibrium i.e. the wage inequality is $\theta_H - \theta_L$ and moreover let us use the intuitive criterion refinement which eliminates all pooling equilibria. Since indifference curves of low type workers become flatter, it is now becomes profitable for them to deviate and to pretend to be workers of high productivity. In this case either firms become unable to distinguish between the types and offer a single wage for all types (pooling equilibrium) and as a result, inequality decreases to 0, or workers of high type just increase their level of education (starting to pursue PhD for example) and firm still are able to distinguish between types and offer different wages, hence the wage inequality remains unchanged.
\section*{7 Equilibrium Refinements}
	There are many different criteria that can be used to refine the set of equilibria in a given
	game. One of them, which you have already discussed, is the intuitive criterion. Think about
	the logic it tries to capture. Can you think of other ways to select reasonable out-of-equilibrium path beliefs? Suggest one such criterion and explain intuitively why it is reasonable. You may
	refer to Beer and Quiche or Education signalling or your own set up to illustrate the logic behind
	your criterion.

	Intuitive criterion and other criteria try to refine unreasonable out-off equilibrium beliefs. For example, in $Beer-and-Quiche$ set-up (Problem 2). Intuitive criterion requires $\lambda$ (the conditional probability of coming across surly type, condition on the fact that Paul has ordered quiche) being equal to 1, because it is unreasonable for wimpish Paul to deviate from equilibrium. It is a good logic, but as for me it does not fully capture reality. In reality there is always a some probability of mistake, moreover Nick cannot for sure know the cost of drinking beer for wimp Paul. That's why I think it would be more reasonable to consider beliefs in unreachable information set as a random variable distributed on $[0, 1]$. It can be beta $B(a, b)$ distribution. Where parameters $a$ and $b$ are chosen taking into account possible payoffs of players. For instance $c$ is very close to 2 then Paul can not care a lot about his order and the probability of mistake becomes higher. However even if $c$ is small Nick cannot rule out the chance that apart from being wimpish Paul is also stupid and orders $quiche$. Thus, the distribution of belief $\lambda \sim B(a, b)$ where parameters are chosen in a special way (if this problem costs more than 5 point maybe I will derive some possible formulas for $a$ and $b$) capture the reality more precisely, in my opinion.
\end{document}
